Place of death in NRS COVID-19 deaths: visualisation for 2022 data

### 2023-07-13 covid_nrs_place_of_death_data_2023.Rmd
small improvements, i guess?

```{r}
merged_proportions_of_deaths_by_place <-
  bind_rows(
    ## 2015-2019
    weekly_deaths_2015_2019_overall %>% 
    group_by(year, place_of_death) %>% summarise(number_of_deaths = sum(number_of_deaths), .groups="drop") %>%
    filter(place_of_death != "All" & !is.na(as.integer(year))) %>%
    group_by(year) %>%
    mutate(
      total_deaths = sum(number_of_deaths)
    ) %>%
    ungroup %>%
    mutate(
      proportion_of_total = number_of_deaths / total_deaths, 
      year=as.integer(year)
      ),
    ## 2020 onwards
    total_deaths_overall %>%
    select(year, place_of_death, number_of_deaths = deaths_all_causes) %>%
    distinct %>%  # remove duplicate entries for 2022 due to having multiple possible historic periods
    filter(place_of_death != "All") %>%
    group_by(year) %>%
    mutate(
      total_deaths = sum(number_of_deaths)
    ) %>%
    ungroup %>%
    mutate(proportion_of_total = number_of_deaths / total_deaths)
  )
```

>>>>

```{r}
merged_proportions_of_deaths_by_place <-
  bind_rows(
    ## 2015-2019
    weekly_deaths_2015_2019_overall %>% 
    group_by(year, place_of_death) %>% summarise(number_of_deaths = sum(number_of_deaths), .groups="drop") %>%
    filter(place_of_death != "All" & !is.na(as.integer(year))) %>%
    group_by(year) %>%
    mutate(
      total_deaths = sum(number_of_deaths)
    ) %>%
    ungroup %>%
    mutate(
      proportion_of_total = number_of_deaths / total_deaths, 
      year=as.integer(year)
      ),
    ## 2020 onwards
    total_deaths_overall %>%
    select(year, place_of_death, number_of_deaths = deaths_all_causes) %>%
    distinct %>%  # remove duplicate entries for 2022 due to having multiple possible historic periods
    filter(place_of_death != "All") %>%
    group_by(year) %>%
    mutate(
      total_deaths = sum(number_of_deaths)
    ) %>%
    ungroup %>%
    mutate(proportion_of_total = number_of_deaths / total_deaths)
  ) %>%
  (function(x) {
    bind_rows(
      x,
      x %>%
        group_by(year) %>%
        summarise(
          place_of_death = "All",
          number_of_deaths = sum(number_of_deaths, na.rm = TRUE),
          total_deaths = unique(total_deaths),
          proportion_of_total = 1
          )
    )
  }) %>%
  mutate(place_of_death = factor(place_of_death, levels = order_of_place_of_death_levels[c(1,3,2,4,5)])) %>%
  arrange(year, place_of_death)

write_csv(x = merged_proportions_of_deaths_by_place, file = file.path(dir_outputs, "annual_deaths_by_place.csv"))
```

### 2023-07-13 covid_nrs_place_of_death_visualisations_2022.Rmd
small improvements, i guess?

actual_and_predicted_data <-
  bind_rows(
    merged_proportions_of_deaths_by_place %>%
    select(year, number_of_deaths, place_of_death) %>%
    filter(place_of_death == "Home & other non-institution" & year %in% 2015:2019) %>%
      mutate(data_type = "Actual")
    ,
    merged_proportions_of_deaths_by_place %>%
    select(year, number_of_deaths, place_of_death) %>%
    filter(place_of_death == "Home & other non-institution" & year %in% 2020:2022) %>%
    mutate(
      data_type = "Predicted",
      number_of_deaths = if_else(year %in% 2020:2022, compute_y_from_x_using_regression(x = year-2015, regression_model = regression_model), number_of_deaths)
      )
    ,
    merged_proportions_of_deaths_by_place %>%
      select(year, number_of_deaths, place_of_death) %>%
      filter(place_of_death == "Home & other non-institution" & year %in% 2020:2022) %>%
      mutate(
        number_of_deaths = if_else(year == 2022, number_of_deaths / extrapolated_2020_data$proportion_of_deaths_so_far, number_of_deaths),
        year = 2015 + compute_x_from_y_using_regression(y = number_of_deaths, regression_model = regression_model),  # compute predicted X
        data_type = "Actual"  # note: this is actual figures but
      )
  )

>>>>

actual_and_predicted_data <-
  bind_rows(
    merged_proportions_of_deaths_by_place %>%
    select(year, number_of_deaths, place_of_death) %>%
    filter(place_of_death == "Home & other non-institution" & year %in% 2015:2019) %>%
      mutate(data_type = "Actual")
    ,
    merged_proportions_of_deaths_by_place %>%
    select(year, number_of_deaths, place_of_death) %>%
    filter(place_of_death == "Home & other non-institution" & year %in% 2020:2022) %>%
    mutate(
      data_type = "Predicted",
      number_of_deaths = if_else(year %in% 2020:2022, compute_y_from_x_using_linear_regression(x = year-2015, regression_model = regression_model), number_of_deaths)
      )
    ,
    merged_proportions_of_deaths_by_place %>%
      select(year, number_of_deaths, place_of_death) %>%
      filter(place_of_death == "Home & other non-institution" & year %in% 2020:2022) %>%
      mutate(
        number_of_deaths = if_else(year == 2022, number_of_deaths / extrapolated_2020_data$proportion_of_deaths_so_far, number_of_deaths),
        year = 2015 + compute_x_from_y_using_linear_regression(y = number_of_deaths, regression_model = regression_model),  # compute predicted X
        data_type = "Actual"  # note: this is actual figures but
      )
  )
